---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Han Zhao"
date: "5/12/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This was built as part of a deliverable for the course Developing **Data Products** as part of the Coursera **Data Science Specialization**.

The app developed for the first part of the assignment demo is avalilable at: <https://hanzhao.shinyapps.io/myapp001/>.

Source code for ui.R and server.R files are available on the GitHub repo: <https://github.com/hanzhaoui/project3>.

## Web Application Functionality

- This app is based on the airquality data set. It utilizes the linear regression model (lm) to fit of the Ozone vs.Temperature datapoints. The Slope and Intersect 
- The user can select the month(s) of interest on the side panel.
- The user can also select of data points of interest on the plot.

## Airquality Data Set
The data used in the app comes from the New York Air Quality Measurements (airquality) dataset. Let has a look on the airquality's summary
```{r plot1}
data("airquality")
summary(airquality)
```

## Snapshot of the App
Here is the snapshot of the web app. 
```{r, echo=FALSE}
library(png)
library(grid)
img <- readPNG("/Users/HanZhao/testdir/rproduct/project3/image.png")
 grid.raster(img)
```

